\myTitle

### 2024-01-08 body-text-of-paper.tex
Eric edited the introduction a bit.

In using clustering algorithms to describe genetic structure among natural populations, researchers frequently identify individuals of
mixed ancestry--- individuals with proportions of their genome attributed to multiple subpopulations, sensu \citet{pritchard2000inference}.
Various processes could contribute to such mixed associations.  Most directly, individuals may represent the
influences of gene flow among populations, occurring in recent or prior generations, with the observed complex ancestry patterns accurately
representing contributions from multiple sampled populations.  However, similar patterns may result from functionally different patterns of
population structuring.  For example, such patterns might be expected when clinal systems governed by isolation by distance are described
as discrete genetic clusters.
Alternatively, individuals of mixed ancestry could reflect immigration from outlying populations (e.g., exogenous immigration), with true source
populations not sufficiently
represented in the sample to be among the characterized $K$ subpopulations.
Furthermore, the characterization of admixed individuals may reflect a limitation of the statistical power of the genetic data,
as a function of both the marker set and sample size, to resolve the true underlying patterns of genetic structure.
 The challenge for researchers then becomes correctly identifying the ecological and/or statistical processes by which observed complex
 ancestry patterns were created.

A best practice for evaluating the behavior of genetic clustering algorithms on an empirical dataset is to conduct
parallel analyses on simulated data where the truth is known, yet structured to mirror the empirical data set
as closely as possible \citep{vaha2006efficiency,anderson2008improved,latch2011fine}.
Techniques to simulate individual genotypes in this context frequently use sampling with replacement from the
observed allele frequencies (see CITE, CITE, CITE).
However, sampling with replacement implicitly increases the pairwise genetic distance among simulated samples, relative to the observed
samples, and
inflates the perceived statistical power to correctly assign individuals back to source populations.
We refer to this phenomenon as resampling-induced, spurious power inflation (RISPI).
\citet{anderson2008improved} used simulations to document this type of artifact in the context of
genetic stock identification (GSI), a type of clustering application in which individuals are constrained to have
all their ancestry from a single subpopulation.
Similar statistical artifacts occur when simulating data to
assess how accurately admixture fractions can be estimated.

Beyond simply evaluating the resolution of discrete populations in a simulated framework, researchers may also be
interested in how individuals of admixed ancestry are genetically characterized given the statistical power of the available dataset and the
analysis methods used.
Recognizing that connectivity among genetically distinct populations may be relatively rare, additional insight into the
frequency of immigration can be gained by integrating across generations to identify both direct migrants and descendants of migrants
 (i.e., F1 hybrids or advanced hybrids reflecting the effect of backcrossing across multiple generations [BC1, \ldots,
BCX]).
However, the process of recombination during meiosis creates a distribution of expected associations to parental populations among
advanced hybrid classes.
Treating linked loci as independent can lead to the false interpretation that the association of advanced hybrid classes to parental population
occur strictly as discrete distributions.
Therefore, in evaluating descendants of migrants within a simulated framework, it is imperative to take into consideration the pattern of
linkage among loci available for analysis.

In response to these needs, we developed \gscramble{} – a simulation approach that samples alleles from respective populations without
replacement, thus maintaining the genetic differences in the empirical dataset and eliminating the effect of RISPI.
Further, by simulating individual genotypes based on user-defined pedigrees, \gscramble{} allows for the simulation of admixed genotypes of
varying degrees of complexity while allowing the tracking of haplotype blocks from source populations within the specified pedigree.
By integrating species-specific recombination rates, \gscramble{} simulates biologically informed genotypes that mirror empirical data.
We develop and illustrate \gscramble{} with use of single nucleotide polymorphic (SNP) genotypes.

@@

Our approach for simulating admixed individuals without inflating perceived power for
the estimation of their admixture fractions is motivated by the traditional cross-validation
approach for evaluating the power of mixture proportion
estimation in genetic stock identification (e.g., the cross-validation approach
described in \citealt{moran2019bayesian}).
In the cross-validation approach, individuals are removed from the reference
samples and placed in a mixture sample of "unknowns", whose origin
is inferred using the remaining individuals in the reference samples.  A key
feature of this approach is that no new genetic material is being created by
sampling with replacement; rather the genetic material of all individuals
in the original sample is being used---either within the remaining individuals in the
reference samples or within the individuals in the mixture.

@@

@@

>>>>

In using clustering algorithms to describe genetic structure among natural populations, researchers frequently identify individuals of
mixed ancestry---individuals with proportions of their genome attributed to multiple subpopulations, sensu \citet{pritchard2000inference}.
Various processes could contribute to the appearance of mixed ancestry in a clustering analysis.  Most directly, individuals may represent the
influences of gene flow among populations, occurring in recent or prior generations, with the observed complex ancestry patterns accurately
representing contributions from multiple sampled populations.  However, similar patterns may result from functionally different patterns of
population structuring.  For example, such patterns might be expected when clinal systems governed by isolation by distance are described
as discrete genetic clusters.
Alternatively, individuals of mixed ancestry could reflect immigration from outlying populations (e.g., exogenous immigration), with true source
populations not sufficiently
represented in the sample to be among the characterized $K$ subpopulations.
Furthermore, the characterization of admixed individuals may reflect a limitation of the statistical power of the genetic data,
as a function of both the marker set and sample size, to resolve the true underlying patterns of genetic structure.
 The challenge for researchers then becomes correctly identifying the ecological and/or statistical processes by which observed complex
 ancestry patterns were created.

A best practice for evaluating the behavior of genetic clustering algorithms on an empirical dataset is to conduct
parallel analyses on data that have been simulated---so the truth is known---so as to mirror the empirical data set
as closely as possible \citep{vaha2006efficiency,anderson2008improved,latch2011fine}.
Techniques to simulate individual genotypes in this context frequently use sampling with replacement from the
observed allele frequencies (see, for example, \citealt{nielsen2006hybridlab,kinziger2008hybridization}).
However, sampling with replacement implicitly increases the pairwise genetic distance among simulated samples, relative to the observed
samples, and
inflates the perceived statistical power to correctly assign individuals back to source populations.
We refer to this phenomenon as resampling-induced, spurious power inflation (RISPI).
\citet{anderson2008improved} used simulations to document this type of artifact in the context of
genetic stock identification (GSI), a type of clustering application in which individuals are constrained to have
all their ancestry from a single subpopulation.
Similar statistical artifacts occur when simulating data to
assess how accurately admixture fractions can be estimated.

Beyond simply evaluating the resolution of discrete populations in a simulated framework, researchers may also be
interested in how individuals of admixed ancestry are genetically characterized given the statistical power of the available dataset and the
analysis methods used.
Recognizing that connectivity among genetically distinct populations may be relatively rare, additional insight into the
frequency of immigration can be gained by integrating across generations to identify both direct migrants and descendants of migrants
 (i.e., F1 hybrids or advanced hybrids reflecting the effect of backcrossing across multiple generations [BC1, \ldots,
BCX]).
Evaluating the results of genetic clustering algorithms in the context of data that are
expected to arrive by such a process of hybridization requires simulation of
explicit hybrids.  Such simulations are the purpose of the software {\sc hybridlab} 
\citep{nielsen2006hybridlab}.

{\sc hybridlab} was conceived at a time when
the data sets used in molecular ecology universally included very few markers, such that
it was reasonable to assume the markers were unlinked, and, hence, independently segregating.
Today, however, with data sets of thousands of markers, that assumption is badly violated---alleles
on the same chromosome are likely to be segregated together into the next generation.
Simulating linked loci as independent creates simulated hybrids, beyond the $F1$ category, with 
artificially low variance in admixture fraction, leading to the false interpretation that different
hybrid categories are more easily distinguished than they are. Therefore, in evaluating descendants of migrants within a simulated framework, it is imperative to take into consideration the pattern of
linkage among loci available for analysis. This was done recently to assess the power of a SNP panel for identifying descendants of escaped, farm-raised Atlantic salmon \citep{wringe2019development}; however the method used (described at https://eriqande.github.io/SalarHybPower/) was developed in an {\em ad hoc} fashion and was not easily extended to
complex hybridization scenarios, and was not at all user-friendly.

In response to these needs, we developed \gscramble{} – a simulation approach that samples alleles from respective populations without
replacement, thus maintaining genetic differences between the clusters commensurate to those in the empirical dataset, and eliminating the effect of RISPI.
Further, by simulating individual genotypes based on user-defined pedigrees of arbitrary complexity, \gscramble{} allows for the simulation of admixed genotypes resulting from any conceivable category of hybrid, while allowing the tracking of haplotype blocks from source populations within the specified pedigree.
By integrating species-specific recombination rates, \gscramble{} simulates biologically informed genotypes that mirror empirical data.
We develop and illustrate \gscramble{} with use of single nucleotide polymorphic (SNP) genotypes, though it is equally applicable to data sets with hundreds or thousands of
microhaplotypes \citep{baetscher2018microhaplotypes} or microsatellites
\citep{zhan2017megasat}.

@@

Our approach for simulating admixed individuals without creating RISPI is motivated by the traditional cross-validation
approach for evaluating the power of mixture proportion
estimation in genetic stock identification (e.g., the cross-validation approach
described in \citealt{moran2019bayesian}).
In the cross-validation approach, individuals are removed from the reference
samples and placed in a mixture sample of "unknowns", whose origin
is inferred using the remaining individuals in the reference samples.  A key
feature of this approach is that no new genetic material is being created by
sampling with replacement; rather the genetic material of all individuals
in the original sample is being used---either within the remaining individuals in the
reference samples or within the individuals in the mixture.

@@

Genotypes for

@@

Also, we need to discuss the fact that, because each time a gamete is segregated in the
pedigree, its complement is also segregated, this is an example of antithetical variate sampling
in Monte Carlo.
